ChemKED: a human- and machine-readable data standard for chemical kinetics experiments

### 2017-10-02 pyked.tex
Clarify human readability as ease of use
In the YAML description section

\ck{} files use the YAML data serialization format~\autocite{yaml:1.2}. This
format offers the advantages of being human readable, written in plain text, and
having parsers in most common programming languages, including Python, C++, Java,
Perl, MATLAB, and many others. The YAML syntax is quite simple: the basic file
structure consists of mappings, delimited by a colon. The key for the mapping is
on the left of the colon, and the value on the right can be a single value,
a sequence of values, a nested mapping, or some combination of these:
%
\begin{yamlbox}
key1: value  # Single-value mapping
key2:  # Sequence format
  - value
  - value
key3:  # Nested mapping
  key4: 0
key5:  # Sequence of mappings
  - key-s1: 0
    key-s2: value
  - key-s2: value
    key-s1: 0
\end{yamlbox}

>>>>

\ck{} files use the YAML data serialization format~\autocite{yaml:1.2}. This
format offers the advantages of being relatively easy for humans to read and write,
encoded in plain text (ASCII or UTF-8 format), and
having parsers in most common programming languages, including Python, C++, Java,
Perl, MATLAB, and many others. The YAML syntax is quite simple: the basic file
structure consists of mappings, delimited by a colon. The key for the mapping is
on the left of the colon, and the value on the right can be a single value,
a sequence of values, a nested mapping, or some combination of these:
%
\begin{yamlbox}
key1: value  # Single-value mapping
key2:  # Sequence format
  - value
  - value
key3:  # Nested mapping
  key4: 0
key5:  # Sequence of mappings
  - key-s1: 0
    key-s2: value
  - key-s2: value
    key-s1: 0
\end{yamlbox}
